Paper

### 2018-11-06 paper.Rmd
paper markdown document

---
title: "Ideas_ntw_function"
author: "I. Bartomeus, A. Magrach"
date: "6/14/2018"
output: html_document
---
---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A & Bartomeus, I"
date: "6 November 2018"
output: html_document
---

-------------------------------------
IDEAS
-------------------------------------

I'll start by 
  - showing the relationship between ntw structure (defined as? Niche complementariety?) and overall functioning (defined as mean rep success of plants?)
  - showing the relationship between node position and plant species functioning
  - showing the relationship between ntw structure and functioning maximization (eveness of fucntioning, well, not evenness, you want equity (that is, even and high))

We can use data on both visitation rates (quantity), pollen deposition (quality), its product (pollen delivered) and fruit set and seed set.

AINHOA OTHER IDEAS: We could look at in the future
1) how do perturbations (in this case fragmentation) affect species specialization? in this setting are specialization and 
link conservatism or opportunism (how regional interaction richness of a species differs from what could be expected if species interacted randomly with the available set of partners, see Carstensen et al 2017) constant through time? Carstensen et al also find that specialization is conserved from local to regional levels (correlation between specialization levels), is this the case in a fragmented setting? 
2) are these changes a consequence of turnover in species composition across fragments or interaction composition (rewiring)? or is it temporal turnover?
3) changes in node position in plants with perturbation. what are the consequences for functioning? seed set

-----------------------------------------
ABSTRACT
-----------------------------------------

@@

-----------------------------------------
QUESTIONS
-----------------------------------------

1) How does network structure, and in particular two aspects (nestedness and functional complementarity), that represent redundancy (and thus potentially resilience to species loss) and complementarity in niche (and thus potentially increased reproductive success through niche differentiation, specialization and increased pollen deposition of same species) link to ecosystem function (mean fruit and seed set) at the community level?

2) How does the node position of a plant species within a network affect ecosystem functioning (here reproductive success)? Apparent competition with other plant species? Pollinator diversity visiting?

3) How does network structure affect equity in functioning?

-----------------------------------------
METHODS
-----------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r, include=TRUE}
#First attempt to load the data, etc...

@@

poll

@@

plant

@@

link

@@

------------------------------------------------------------------------------------------------------
QUESTION 1:  - relationship between ntw structure defined as nestedness (i.e. redundancy) and complementarity (i.e. funct compl), also taking into species-level characteristics (e.g., degree and specialization) and relate it to overall functioning (defined as mean rep success of all plant species together per site)
------------------------------------------------------------------------------------------------------

```{r, include=TRUE}

#####################################################################################################################
######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
######################################################################################################################
#calculate column with fruit set as

@@

head(out.site)
str(out.site)
c<-cor(out.site[,2:20])
c2<-round(c,digits=2)
#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")

@@

tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})

@@

@@

tableSx2 <- aggregate(Fruit.nÂº ~ Site_ID + Plant.sp + Plant.ID, data = s, FUN = function(x){NROW(x)})

@@

#it seems all effects are driven by Cistus ladanifer, re-analyse without this species

```{r, include=TRUE}
s.agg2<-subset(s.agg, s.agg$Plant.sp!="Cistus ladanifer")

@@

pl5

interact_plot(m2.see.2, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
              modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
```
#driven only by C. salvifolius and albidus? re-do analyses

```{r, include=TRUE}

@@

pl7

@@

pl8

@@

pl9

# 
# ggplot(out.site,  aes(x= nodf.song, y=functional.comp.poll))+      
#         geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
#         geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
#         xlab("Nestedness") +      
#         ylab("Functional compl") + theme_bw()  
# 
# 
# summary(lm(functional.comp.poll ~ nodf.song, data=s.agg4))$r.squared

#SEED WEIGHT

@@

#RELATIONSHIP BETWEEN NODE POSITION AND FUNCTIONING

#look at cz plots to see potential connector, hub etc species

```{r, include=TRUE}

@@

@@

#for pollinator species

@@

#LOOK AT EVENNESSS IN FUNCTION. within a site most plant species have very low reproductive success and thus we get incredibly high evenness values. therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production

```{r, include=TRUE}
library(vegan)
library(dplyr)

@@

f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
f5<-subset(f4, f4$fruit.prop>0.5)

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<-f5 %>% 
  group_by(Site_ID) %>%
  summarise(no_rows = length(Site_ID ))

@@

#look at single visit data for some species to see whether they can be related to network roles or repr success
#importante

#Control = siempre embolsados
#Open = embolsados la noche antes, y open durante 6 horas de dia (o sea visitado por lo que sea que pasara durante el dia).

```{r, include=TRUE}

# si.cs<-subset(si, si$Plant.sp=="Cistus  salvifolius") 
# si.cs
# 
# 
# pl.si.cs<-ggplot(si.cs,  aes(x=Pollinator_genus, y=pollen_tubes))+  
#   geom_bar(stat="identity")
#         
# pl.si.cs

library(ggplot2)

gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}

mycols <- gg_color_hue(length(unique(si$Pollinator_genus)))
names(mycols) <- unique(si$Pollinator_genus)
mycols["Control"] <- "black"
mycols["Open"] <- "grey"
mycols["Apis"] <- "yellow"

  pl.si<- ggplot(si,  aes(x=Pollinator_genus, y=pollen_tubes, fill=Pollinator_genus))+  
    geom_bar(stat="identity")  + scale_fill_manual(values=mycols) + theme (legend.position= "none") #+ 
    # theme(text = element_text(size = 12),
    #     axis.text=element_text(size=rel(1)),
    #     axis.title=element_text(size=rel(1),face="bold"), legend.direction="horizontal", legend.text=element_text(size=10))

  pl.si + facet_wrap( ~ Plant.sp, scales="free")

El control tiene valores super altos, esta bien?? COntrol es el negro, open el gris

>>>>

---
title: "Paper"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
---

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A & Bartomeus, I"
date: "6 November 2018"
output: html_document
---

# ABSTRACT

@@

#INTRODUCTION

# METHODS

@@

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=9}
#First attempt to load the data, etc...

@@

#poll

@@

#plant

@@

#link

@@

### QUESTION 1:  
What is the relationship between network structure and functioning?

Here, we will define network structure at the community (whole-network level) focusing in particular in two aspects: network nestedness (a measure of redundancy in species roles) and functional complementarity (a measure of complementarity in species niches). Functioning will be defined as average fruit set for each species at each site. Plant species will be included as a random factor to evaluate whether the reproductive success of different species change across networks with different overall structures. Models include nestedness, funct compl and their interaction. check best model with "dredge" and plot significant variables

#### Function as FRUITSET

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#####################################################################################################################
######################## NTW STRUCTURE ~ ECOSYSTEM FUNCTION #########################################################
######################################################################################################################
#calculate column with fruit set as

@@

#head(out.site)
#str(out.site)
c<-cor(out.site[,2:20])
c2<-round(c,digits=2)
#write.csv(c2, file= "~/Dropbox/Beefun/Beefun/functioning/tables/variable_correlations.csv", row.names = TRUE, sep = ",")

@@

#tableSx <- aggregate(Plant.ID ~ Site_ID + Plant.sp, data = f2, FUN = function(x){NROW(x)})

@@

```
#### Function as SEED NUMBER

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

#tableSx2 <- aggregate(Fruit.nÂº ~ Site_ID + Plant.sp + Plant.ID, data = s, FUN = function(x){NROW(x)})

@@

it seems all effects are driven by Cistus ladanifer, re-analyse without this species

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
s.agg2<-subset(s.agg, s.agg$Plant.sp!="Cistus ladanifer")

@@

#pl5

interact_plot(m2.see.2, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
              modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))
```

driven only by C. salvifolius and albidus? re-do analyses

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

#pl7

@@

#pl8

@@

#pl9

# 
# ggplot(out.site,  aes(x= nodf.song, y=functional.comp.poll))+      
#         geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
#         geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
#         xlab("Nestedness") +      
#         ylab("Functional compl") + theme_bw()  
# 
# 
# summary(lm(functional.comp.poll ~ nodf.song, data=s.agg4))$r.squared
```

#### fUNCTION AS SEED OR FRUIT WEIGHT

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

### QUESTION 2:  
2) How does the position of a plant species within a network affect its reproductive success?

We will focus on the effect of networks metrics measured at the species level: normalised degree, c, z, betweenness and closeness on average fruit set per plant. This time site will be included as random to evaluate whether node position of a plant species in a particular networks affects its reproductive success.

look at cz plots to see potential connector, hub etc species, first for all plant species in the network, then only for species for which we have data on fruit set

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

remove C. ladanifer which seems to be driving the relationship

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

look at cz plots for pollinator species. triangles are apis mellifera, potential there for study on their effect for repr success??

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

@@

### QUESTION 3:

How does network structure affect equity in functioning?

LOOK AT EVENNESSS IN FUNCTION. within a site most plant species have very low reproductive success and thus we get incredibly high evenness values. therefore we use thresholds, for each sps and site we calculate the # of individuals that are above 50% in fruit production

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}

library(vegan)
library(dplyr)

@@

f4$fruit.prop<-f4$mean.fruitset/f4$fruit.max
f5<-subset(f4, f4$fruit.prop>0.5)
f5$no_rows<-rep(1, nrow(f5))

#for each site here is the number of sps whose fruitset exceeds 50% of maximum fruitset observed in the whole study area
f6<- aggregate(no_rows ~ Site_ID, f5, length)

@@
